---
title: "Election"
author: "Tanish Thaker"
format: html
execute: 
  echo: false
---

```{r}
#| message: false
#| label: setup

library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)

x <- governors |> 
  select(death_age, election_age, win_margin, party, sex) |> 
  mutate(treatment = ifelse(win_margin > 0, "win", "lose")) |> 
  filter(abs(win_margin) < 5) |>
  drop_na()
```

```{r}
#| cache: true

fit_model <- brm(formula = death_age ~ election_age + treatment + party + sex,  
             data = x,
             family = gaussian(),
             refresh = 0,
             silent = 2,
             seed = 99)
```

```{r}
pp_check(fit_model)

fixef(fit_model)
```


Question: How long will Preceptor live to if he wins the election for mayor of Newton?

Units: People who ran for mayor

Outcome: death_age

Model Type: Causal Model

Covariates: election_age

Treatment: Winning the Election

Validity: Might not hold because different states have generally different life expectencies. 

Population Table-

Units: People who ran for governor

Outcome: death_age

Covariates: Sex, election_age

Stability: Life expectencies change as time passes

Representativness: Data doesn't represent states and not cities

Unconfoundedness: Outside factors lead males to be elected more frequently

Final Paragraph: 
